Logarithmic Space Verifiers on NP-complete

### 2019-11-12 doc/manuscript.tex
Updated the content proof

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\] 
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes less than $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $k \times n$ symbols for some arbitrary number $k > 1$ which mostly depends from the original instance, that is the result of reading consecutively the symbols in the input tape in a sequential way. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $k \times n$. However, we know in that instance of size at most $k \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right. Therefore, the instance of size at most $k \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with less than $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language. In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{k})]$ for some arbitrary number $k > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{k})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{k})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{k})]$ under our supposition. Since $T'(n)$ is not equal to $T'(\frac{n}{k})$ for some arbitrary number $k > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every sparse function $T(n)$.
\end{proof}

>>>>

\begin{proof}
Suppose that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction for some $T'(n)$ when
\[\lim_{n\to\infty} \frac{T'(n)}{n} = 0.\]
Hence, the family of languages $\textit{1TAPE}[T'(n)]$ is two-way logarithmic space reduced to the another family of languages $\textit{1TAPE}[T'(n) - H(n)]$ where the deterministic two-way logarithmic space reduction consumes less than $H(n)$ in the work tapes. Consequently, for each instance of a language in $\textit{1TAPE}[T'(n)]$ of size $n$, then this could be equivalent to another instance of size with at most $k \times n$ symbols for some constant $k > 1$, that is the result of reading consecutively the symbols in the input tape in a sequential way. This means if during the deterministic two-way logarithmic space reduction the input head moves to the left or to the right, then this is a new symbol that appears contiguously to the right in the instance of size at most $k \times n$. However, we know in that instance of size at most $k \times n$, we can replace the deterministic two-way logarithmic space reduction by a deterministic one-way logarithmic space reduction that read contiguously from left-to-right. Therefore, the instance of size at most $k \times n$ could be decided by a deterministic one-way logarithmic space Turing machine that simulates the two-way logarithmic space reduction with less than $H(n)$ in the work tapes within the composition on the another deterministic one-way logarithmic space Turing machine which is used in $\textit{1TAPE}[T'(n) - H(n)]$ after the deterministic two-way logarithmic space reduction of the original language. In this way, we obtain that the family of languages of $\textit{1TAPE}[T'(n)]$ is contained into the family of languages $\textit{1TAPE}[T'(\frac{n}{k})]$ for some constant $k > 1$ under the assumption that $\textit{1TAPE}[T'(n)]$ is not closed under deterministic two-way logarithmic space reduction. As result, we obtain that $\textit{1TAPE}[T'(n)] = \textit{1TAPE}[T'(\frac{n}{k})]$ since we previously know that $\textit{1TAPE}[T'(\frac{n}{k})] \subseteq \textit{1TAPE}[T'(n)]$ and we show that $\textit{1TAPE}[T'(n)] \subseteq \textit{1TAPE}[T'(\frac{n}{k})]$ under our supposition. Since $T'(n)$ is not equal to $T'(\frac{n}{k})$ for some constant $k > 1$, then we obtain that necessarily $\textit{1TAPE}[T'(n)]$ should be closed under deterministic two-way logarithmic space reduction by the reductio ad absurdum logic rule \cite{FE16}. In general, we can assume the same result for every sparse function $T(n)$.
\end{proof}
